manuscript

### 2021-03-09 reports/manuscript.Rmd
Manuscript update

@@

The questionnaire aimed at assessing patients’ subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the standard treatment and the VEs program in either of the five categories (see table XXX). Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`.

@@

dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
knitr::kable(as.data.frame(res),
             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")
```

@@

@@

>>>>

n_vr <- sum(!is.na(df_questionnaire$vr_benefit))
n_paper <- sum(!is.na(df_questionnaire$paper_fun))

@@

The questionnaire aimed at assessing patients’ subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the standard treatment and the VEs program in either of the five categories (see table XXX). `r n_vr` participants answered the questions about the VR portion of the program and `n_paper` about the standard treatment. Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`.

@@

lmer_celek <- temp_mixed_func("dim_celek")
lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
lmer_pozornost <- temp_mixed_func("dim_pozornost")
lmer_rec <- temp_mixed_func("dim_rec")
lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")

```

@@

```{r rbans czech norms, eval=FALSE}
df_rbans_long %>%
  filter(grepl("iq_", subtest)) %>%
  ggplot(aes(subtest, score, fill = factor(session))) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position  = "top", legend.direction = "horizontal")

df_rbans_long %>%
  filter(grepl("dim_", subtest)) %>%
  ggplot(aes(subtest, score, fill = factor(session))) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position  = "top", legend.direction = "horizontal")

df_rbans_long %>%
  filter(!grepl("(iq|dim)_", subtest)) %>%
  ggplot(aes(subtest, score, fill = factor(session))) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position  = "top", legend.direction = "horizontal")

temp_mixed_func <- function(varname){
  out <- df_rbans_long %>%
    filter(subtest == varname, session > 1) %>%
    lmer(score ~ trenink + factor(session) + (1|rbansid), data = .)
  return(out)
}

temp_glm_func <- function(varname){
  out <- df_rbans_long %>%
    filter(subtest == varname) %>%
    glm(score ~ session, data = .)
  return(out)
}

summary(temp_mixed_func("iq_celek"))
summary(temp_glm_func("iq_rec"))
```

@@

```{r}
df_rbans_long %>%
  filter(grepl("iq_", subtest)) %>%
  mutate(session = paste0("session ", session - 1)) %>%
  ggplot(aes(subtest, score, fill = trenink)) +
    geom_boxplot()
```
